### 2015-11-05 section/0_intro.tex
shrinking

Performance bugs\footnote{We also refer performance bugs as performance problems
following previous works in this area~\cite{PerfBug,Alabama,SongOOPSLA2014}} 
are software implementation mistakes that cause unnecessary performance
degradation in software. They widely exist in deployed software due to the 
complexity of modern software and the lack of testing support
~\cite{s2e,PerfBug,perf.fse10,rily.perftest,perfantipattern,xiao13:context}. 
They annoy end users and waste energy during production runs, and 
have already caused highly publicized failures~\cite{ACA-health,colorado}.
Tools that can help
developers quickly and accurately diagnose performance problems,
find performance-wasting root causes, and fix performance problems
are sorely desired.

Like general failure diagnosis, 
performance diagnosis starts from studying a problem symptom and hopefully ends
at identifying the root cause and suggesting a fix strategy. 
In the context of performance problems,
the symptom is often
an execution showing severe absolute or
relative slowness \cite{SongOOPSLA2014}; the root cause contains 
information like which code region is inefficient and why
it is inefficient. An effective diagnosis tool can help developers quickly
and correctly figure out a patch to fix the performance problem.

Also like general failure diagnosis, ideal performance diagnosis tools should
satisfy three criteria.
\begin{itemize}
\item Coverage. 
Real-world performance problems are caused by a wide variety of reasons. It 
would be good if the diagnosis tool can cover a good portion of common
root causes of real-world problems.

\item Accuracy. 
The accuracy requirement applies for two aspects of performance diagnosis: (1)
the inefficient code regions need to be accurately located and (2)
the reason a specific region is inefficient needs to be accurately
explained, so that developers can quickly fix the performance problem.

\item Performance. 
Diagnosis often requires collecting run-time information. The lower the overhead
is, the easier for the diagnosis tool to be deployed, especially for 
production-run usage scenarios. 
\end{itemize}

Although progress has been made, no existing tools can satisfy the above
three requirements.

Profiling is the state of practice in performance diagnosis.
It is far from providing the desired \textit{accuracy}, as it is designed to
tell where computation resources are spent, 
but not where and why computation resources are wasted. 
In many cases, the root-cause function of a performance problem may not even
get ranked by a profiler \cite{SongOOPSLA2014}.

Performance bug detection tools use static or dynamic analysis to identify
code regions that match specific inefficiency patterns 
\cite{Alabama,CARAMEL, Cachetor,Xu:2010:FLD:1806596.1806617,Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616}. 
Unfortunately, these tools are not designed for performance diagnosis.
Consequently, they are not designed to provide \textit{coverage} for a wide
variety of real-world performance problems; they do not target a specific
performance symptom, and hence are at disadvantage in terms of diagnosis
\texttt{accuracy}; dynamic performance-bug detection tools often lead to 
10X slowdowns or more \cite{Cachetor,Xu:2010:FLD:1806596.1806617,Alabama}, 
not ideal in terms of \textit{performance}.

Recently, progress has been made on applying statistical debugging to 
performance diagnosis \cite{SongOOPSLA2014}. Given the symptom of 
a performance problem (e.g., two similar inputs leading to very
different execution speed),
statistical debugging, an approach widely used for diagnosing
functional failures \cite{liblit03,liblit05,tarantula1}, can
accurately identify control-flow constructs that are most correlated with
the performance problem by comparing problematic runs and regular runs.
Unfortunately, for loop-related 
performance problems, which contribute to two thirds of
real-world performance problems studied in previous work 
\cite{SongOOPSLA2014,PerfBug}, statistical debugging is not very effective.
Although it can identify the root-cause loop, it does not provide any 
information regarding why the loop is inefficient and hence is not very helpful
in fixing the performance problem.

@@

\Tool targets the most common type of performance problems, inefficient
loops, according to previous
empirical studies \cite{SongOOPSLA2014,PerfBug}.
\Tool also targets a challenging problem. Although
statistical debugging \cite{SongOOPSLA2014}
can help identify suspicious loops that are highly correlated with 
user-perceived performance problems,
it provides no information about why the suspicious loop is inefficient,
not to mention providing fix suggestions. Although various
bug-detection techniques \cite{Cachetor,Alabama,CARAMEL} can help detect
loop-related performance bugs, they all suffer from generality problems,
covering only a specific type of loop problems each; the dynamic
tools \cite{Cachetor,Alabama} also suffer from performance
problem, imposing 10X slowdown or more.

@@

\item Root-cause taxonomy guided design. To provide the needed coverage, we follow
the root-cause taxonomy discussed above and design analysis routines for 
every root-cause sub-category. Given a candidate inefficient loop, we will 
apply a series of analysis to it to see if it matches any type of inefficiency.
%We will also put the analysis results from different analysis routines together
%to figure out the most likely root cause category for an inefficient loop.

@@

We have evaluated \Tool on 18 real-world performance problems. 
Evaluation results show that \Tool can accurately identify the detailed
root cause for all benchmarks and provide correct fix-strategy suggestion for
16 benchmarks. All these are achieved with low run-time overhead.

>>>>

Performance bugs\footnote{We also refer performance bugs as performance problems
following previous works in this area~\cite{PerfBug,Alabama,SongOOPSLA2014}} 
are software implementation mistakes that cause unnecessary performance
degradation in software. They widely exist in deployed software due to the 
complexity of modern software and the lack of performance testing support
~\cite{s2e,PerfBug,perf.fse10,rily.perftest,perfantipattern,xiao13:context}. 
They annoy end users and waste energy during production runs, and 
have already caused highly publicized failures~\cite{ACA-health,colorado}.
Tools that can help
developers quickly and accurately diagnose performance problems
are sorely desired.

Like general failure diagnosis, 
performance diagnosis starts from studying a problem symptom and hopefully ends
at identifying the root cause and suggesting a fix strategy. 
In the context of performance problems,
the symptom is 
execution 
slowness \cite{SongOOPSLA2014}; the root cause is about
which code region is inefficient and why.
An effective diagnosis tool can help developers quickly
and correctly figure out a fix to the performance problem.

Also like general failure diagnosis, ideal performance diagnosis tools should
satisfy three criteria.
\begin{itemize}
\item Coverage. 
Real-world performance problems are caused by a wide variety of reasons.
A good diagnosis tool should handle a good portion of them.

\item Accuracy. 
First, the inefficient code regions need to be accurately located.
Second, the reason a specific region is inefficient needs to be accurately
explained, so that developers can fix the problem.

\item Performance. 
Diagnosis often requires collecting run-time information. The lower the overhead
is, the easier for the diagnosis tool to be deployed, especially for 
production-run usage. 
\end{itemize}

No existing tools can satisfy these
three requirements.

Profiling is the state of practice in performance diagnosis.
It is far from providing the desired \textit{accuracy}, as it is designed to
tell where computation resources are spent, 
but not where and why resources are wasted. 
In many cases, the root-cause function may not even
get ranked by the profiler \cite{SongOOPSLA2014}.

Performance bug detection tools use static or dynamic analysis to identify
code regions that match specific inefficiency patterns 
\cite{Alabama,CARAMEL, Cachetor,Xu:2010:FLD:1806596.1806617,Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616,IsilDillig.PLDI15}. 
Unfortunately, these tools are not designed for and are consequently
unsuitable for performance diagnosis.
They are not designed to provide \textit{coverage} for a wide
variety of real-world problems; their analysis is not guided by
performance failure symptom, and hence are at disadvantage in terms of diagnosis
\texttt{accuracy}; dynamic detection tools often lead to 
10X slowdowns or more \cite{Cachetor,Xu:2010:FLD:1806596.1806617,Alabama}, 
not ideal in terms of \textit{performance}.

Recently, progress has been made on statistical debugging for
performance diagnosis \cite{SongOOPSLA2014}.
Statistical debugging, an approach widely used for diagnosing
functional failures \cite{liblit03,liblit05,tarantula1}, can
accurately identify control-flow constructs that are most correlated with
the performance problem by comparing runs with and without problematic 
performance.
Unfortunately, for loop-related 
performance problems, which contribute to two thirds of
real-world performance problems studied in previous work 
\cite{SongOOPSLA2014,PerfBug}, statistical debugging is not very effective.
Although it can identify the root-cause loop, it does not provide any 
information regarding why the loop is inefficient and hence is not very helpful
in fixing the performance problem.

@@

\Tool targets the most common type of performance problems, inefficient
loops, according to previous
empirical studies \cite{SongOOPSLA2014,PerfBug}.
\Tool also targets a challenging problem. Although
statistical debugging \cite{SongOOPSLA2014}
can help identify suspicious loops that are highly correlated with 
user-perceived performance problems,
it provides no information about whether and why 
the suspicious loop is inefficient,
not to mention providing fix suggestions. Although various
bug-detection techniques \cite{Cachetor,Alabama,CARAMEL} can help detect
loop-related performance bugs, they all suffer from generality problems,
covering only a specific type of loop problems each; the dynamic
tools \cite{Cachetor,Alabama} also suffer from performance
problem, imposing 10X slowdown or more.

@@

\item Root-cause taxonomy guided design. To provide the needed coverage, we follow
the root-cause taxonomy discussed above and design analysis routines for 
every root-cause sub-category. Given a candidate loop, we will 
apply a series of analysis to it to see if it matches any type of inefficiency.
%We will also put the analysis results from different analysis routines together
%to figure out the most likely root cause category for an inefficient loop.

@@

We have evaluated \Tool on 18 real-world performance problems. 
Evaluation results show that \Tool can accurately identify detailed
root cause for all benchmarks and provide correct fix-strategy suggestion for
16 benchmarks. All of these are achieved with low run-time overhead.

### 2015-11-05 section/1_under.tex
shrinking

The first task we are facing is to figure out a root-cause taxonomy for
real-world inefficient loops. 
Our taxonomy design is guided by checking a benchmark suite of real-world
inefficient loops, collected by previous work \cite{SongOOPSLA2014,PerfBug}. 
We also try to satisfy three requirements in our design.
(1) Coverage: covering
a big portion of real-world inefficient loop problems; 
(2) Actionability: each root-cause category should be informative enough 
to help developers
decide how to fix a performance problem; 
(3) Generality: too application-specific root causes will not work, as we
need to build diagnosis tools to automatically identify these root causes 
without developers' help.
In this section, we will first present our taxonomy, together with real-world
examples, followed by our empirical study about how a suite of real-world 
inefficient
loop problems fall into our root-cause categories.

We should note that we are definitely not the first one who tries to categorize
the root-cause patterns of performance problems. We are also not the first
to identify many of the root-cause categories below. Instead, guided by
previous work and our empirical study, we try to figure out our own taxonomy 
that satisfy the above three requirements and can
work well with the diagnosis tool that we will build later.

>>>>

The first task we are facing is to figure out a root-cause taxonomy for
real-world inefficient loops. 
Our taxonomy design is guided by checking a benchmark suite of real-world
inefficient loops, collected by previous work \cite{SongOOPSLA2014,PerfBug}. 
We also try to satisfy three requirements in our design.
(1) Coverage: covering
a big portion of real-world inefficient loop problems; 
(2) Actionability: each root-cause category should be informative enough 
to help developers
decide how to fix a performance problem; 
(3) Generality: too application-specific root causes will not work, as we
need to build diagnosis tools to automatically identify these root causes 
without developers' help.

Note that we are not the first one who tries to categorize
the root causes of performance problems. We are also not the first
to identify many of the root-cause categories below. Instead, guided by
previous work and our empirical study, we try to figure out our own taxonomy 
that satisfy the above three requirements and can
work well with the diagnosis tool that we will build later.

### 2015-11-05 section/2_workless.tex
shrinking

\section{\Tool design}
\label{sec:design}
\Tool is composed of a series of analysis routines, each designed to 
identify whether a given loop belongs to one specific type of root causes,
as we will present below.

As briefly mentioned in Section \ref{sec:intro}, the design of these analysis routines follows the following principles.
\begin{itemize}
\item Providing diagnosis information, not detecting bugs. \Tool will be  
used together with other performance diagnosis tools \cite{SongOOPSLA2014}
and focus on a small
number of loops that are most correlated with a specific performance symptom,
instead of being applied to the whole program. Therefore, we will have different
design trade-offs in terms of coverage and accuracy, comparing with 
bug detection tools.

\item Static-dynamic hybrid analysis. As we will see, static analysis alone
will not be able to provide all the needed information for performance
diagnosis; dynamic analysis alone will incur too much unnecessary overhead.
Therefore, we will use static-dynamic hybrid approach throughout our design.

\item Using sampling to decrease run-time overhead. Loop-related 
performance problems have the unique nature of repetitiveness, which make 
them a natural fit for random sampling. Therefore, we will design different
sampling schemes for different analysis routines.
\end{itemize}

@@

We consider side-effect instructions as those instructions that write to
variables defined outside the loop. The analysis to identify side-effect
instructions is straightforward. We consider all functions that are called
by a loop directly or indirectly --- a function $F$ that updates variables
defined outside $F$ makes the corresponding call statement in $F$'s
caller a side-effect instruction.
We consider all library functions or function calls through function pointers 
as functions that have side effects, 
unless the library functions are specially marked by us in a white list.

After identifying side-effect instructions, it is straight-forward to
categorize loops into the four types discussed above.
Loop 0* contains no side-effect instructions. 
Loop 1* contains at least one side-effect instruction along every path that
starts from the loop header and ends at the loop header.
The remaining cases are either 
0*1? or [0$|$1]*. 
Differentiating these two cases is also straight-forward.
In short, when the basic block that contains side-effect instructions
is part of the natural loop, the case
belongs to [0$|$1]*; instead, if the side-effect basic block is post-dominated
by one of the loop-exit blocks and is dominated by the loop header, yet is
not part of the natural loop, the case belongs to 0*1?.

@@

Except for 0*, none of the other three type of loops are inefficient for sure.
We need dynamic analysis to figure out what portion of loop iterations are
resultless at run time, which will help decide whether the loop is indeed
the root cause of a user-perceived performance problem and worth fixing.

For a 0*1? loop, since it only generates results in the last iteration, we 
only need to know the total number of iterations (or the average total number 
of iterations when the loop has multiple instances) to figure out the 
\textit{resultless rate} of the loop. The implementation is straightforward
--- we initialize a local counter to be 0 in the pre-header of the loop; we 
increase the counter by 1 in the loop header to count the number of 
iterations; we dump that counter to log when the loop exits.

>>>>

\section{\Tool design}
\label{sec:design}
\Tool is composed of a series of analysis routines that
identify whether a given loop belongs to any root cause type discussed in
Section \ref{sec:study_tax}.
Its design
follows the following principles.
\begin{itemize}
\item Failure diagnosis, not bug detection. \Tool will be  
used together with other performance diagnosis tools \cite{SongOOPSLA2014}
and focus on a small
number of loops that are most correlated with a specific performance symptom,
instead of being applied to the whole program. Therefore, we will have different
design trade-offs in terms of coverage and accuracy, comparing with 
bug detection tools.

\item Static-dynamic hybrid analysis. As we will see, static analysis alone
will not be able to provide all the needed information. However, 
dynamic analysis alone will incur too much overhead.
Therefore, we use a hybrid approach throughout our design.

\item Sampling. Loop-related 
performance problems have the unique nature of repetitiveness, which make 
them a natural fit for random sampling. We will design different
sampling schemes for different analysis.
\end{itemize}

@@

\Tool first identifies side-effect instructions that write to
variables defined outside the loop. 
\Tool analyzes all functions that are called
by a loop directly or indirectly --- a function $F$ that updates variables
defined outside $F$ makes the corresponding call statement in $F$'s
caller a side-effect instruction.
We consider all library functions or function calls through function pointers 
as functions that have side effects, 
unless the library functions are specially marked by us in a white list.

\Tool then categorizes loops into four types.
Loop 0* contains no side-effect instructions. 
Loop 1* contains at least one side-effect instruction along every path that
starts from the loop header and ends at the loop header.
For the remaining cases, 
when the basic block with side-effect instructions
is part of the natural loop, the case
belongs to [0$|$1]*; instead, if the side-effect basic block is post-dominated
by one of the loop-exit blocks and is dominated by the loop header, yet is
not part of the natural loop, the case belongs to 0*1?.

@@

Except for 0*, none of the other three type of loops are inefficient for sure.
We need dynamic analysis to figure out what portion of loop iterations are
resultless at run time, which will help decide whether the loop worths fixing.

For a 0*1? loop, since it only generates results in the last iteration, we 
only need to know the total number of loop iterations 
to figure out the 
\textit{resultless rate} of the loop. The implementation is straightforward
--- we initialize a local counter to be 0 in the pre-header of the loop; we 
increase the counter by 1 in the loop header to count the number of 
iterations; we dump that counter to log when the loop exits.

### 2015-11-05 section/3_redundancy.tex
shrinking

\emph{How to judge redundancy between two iterations/loop-instances?}
Given two iterations (or loop-instances) $i_1$ and $i_2$, since they have 
the same source code, 
a naive, yet expensive, solution is to record and compare the return value of
every memory read conducted by $i_1$ and $i_2$. Two better alternative
solutions are to record and compare only the values written or read by the
side-effect instructions, such as 
line 9 in Figure~\ref{fig:Mozilla477564},
or the source instructions\footnote{We define source instructions in a code
region $r$ as a set of memory-read instructions that side-effect
instructions in $r$ depend on and do not depend on any other instructions
inside $r$.}, 
such as source[i] at line 12 of Figure~\ref{fig:Apache34464}.

Among the the above two potential solutions, our design chooses the second one.
The reason is that, if there is indeed
redundancy, repetitive patterns at the side-effect instructions are caused by
repetitive patterns in the source instructions.
For the purpose of performance diagnosis, it is
more informative to track the cause, rather than the effect.

\emph{How to handle partial redundancy?}
In practice, redundant loops may be doing largely the same, instead of exactly
the same, computation across iterations or loop instances. It is also possible
%TODO define loop instance.
that only some, instead of all, iterations in a loop are doing redundant
computation. We will discuss how we handle this issue in Section \ref{sec:cal}.

\emph{How to lower the overhead of record-and-compare?}
Even if we only record and compare the values returned by source instructions,
instead of all instructions in a loop, the run-time overhead and the log size
would still be large. We will use two ways to lower this time and spatial
overhead. First, static analysis can already tell some source instructions
will always return the same value across iterations/loop-instances, and hence
need not be traced at run time. Second, we can leverage the repetitive nature
of performance problems and use random sampling to lower the overhead without
degrading the diagnosis capability. We will discuss details of 
these two optimization in Section \ref{sec:inst} and \ref{sec:perf}.
%TODO static analysis alone is not sufficient, because some redundant is
%workload dependent

\emph{How to provide the most suitable fix-strategy suggestion?}
Finally, as discussed in Section \ref{sec:study_ob} and Table \ref{tab:root},
memoization and batching are both common fix strategies for redundant loops.
To pick the right fix strategies to fix a redundant loop, we will conduct 
some extra analysis. We will discuss this in Section \ref{sec:redundant_fix}.

@@

After identifying source instructions, we instrument these source
instructions, so that the values returned by these memory read
instructions can be recorded at run time. Specifically, we will assign
a unique ID for each source instruction, and a pair of $<InstID, Value>$
will be recorded at run time with the execution of a source instruction.
Our trace also includes some delimiters and meta information that allows
trace analysis to differentiate values recorded from different loop
iterations, different loop instances, and so on.
%TODO
%All values defined outside the loop is recorded in block O. 
%We record a delimiter, loop instance number and values defined in previous iterations in block H1'.
%Since we only consider redundant iterations from the same loop instance,  
%we do not record values defined outside the loop for cross-iteration redundancy.

@@

\paragraph{High-level algorithms}
For cross-iteration redundancy, we need to answer two questions. 
First, how to judge whether
two iterations are doing redundant work --- should the two iterations conduct
exactly the same computation?
Second, is a (dynamic) loop problematic when it contains only few 
iterations that are
redundant with each other?

Our answer to these two questions stick to one principle: there should be
sufficient amount of redundant computation to make a loop likely root-cause
for a user-perceived performance problem and to make itself worthwhile to
get optimized by the developers. Consequently,
for the first question, \Tool takes a strict 
definition --- only iterations that are doing exactly the same computation are
considered redundant. Since one iterating may not contain too much computation,
a weaker definition here may lead to many false positives. For the 
second question, we believe there should be a threshold. In our current 
prototype,
when the number of distinct iterations is less than half of the total iterations, 
we consider the loop is cross-iteration redundant. 
%when the number of distinct iterations is less than half of the total iterations 
%iterations/(distinct iterations) = 2

@@

For example, Figure~\ref{fig:Apache37184} shows a loop from Apache-Ant that
contains cross-iteration redundancy.
As we can see, under the problem triggering input, 
only several distinct listeners are contained inside the vector, and most of 
iterations of the loop inside function \texttt{fireMessageLoggedEvent}
are doing exactly the same computation. 
%The problem for this bug is that developers say that the performance 
%loss happens in fireMessageLoggedEvent, but in the code I found, function
%messageLogged does not contain anything, and it is an empty function.
%I guess either developers do not have correct understanding of this bug,
%or I did not find the correct codes.

@@

The implementation of checking cross-loop redundancy goes through several
steps. First, for $k$ dynamic instances of a static loop $L$ that appear
at run time, denoted as $l_1$, $l_2$,
..., $l_k$, we check whether redundancy exists between $l_1$ and $l_2$, 
$l_2$ and $l_3$, and so on. Second, we compute a 
\textit{cross-loop redundancy rate} for $L$
--- dividing the number of redundant pairs by $k-1$.
The smaller the rate is, with 0 being the minimum possible value, the
less cross-loop redundancy $L$ contains.
Here we only check redundancy between consecutive loop instances, because  
checking the redundancy between every pairs of loop
instances would be very time consuming.

@@

\paragraph{Cross-loop redundancy analysis} 
At high level, we randomly decide at the beginning
of every loop instance whether to track values for this instance. 
Since we will need to compare two consecutive loop
instances for redundancy, once we decide to sample one loop instance, we will
make sure to sample the immediately next loop instance too.

The implementation is similar with that for cross-iteration redundancy analysis.
The only difference includes: (1) clone is made for the whole loop and the
sampling control
is done in the pre-header of the loops; (2)
sampling is conducted when \texttt{CurrentID} equals either
\texttt{NextSampleID} or \texttt{NextSampleID}$+1$, with \texttt{NextSampleID}
increased by a random value in the latter case.

@@

\paragraph{Handling recursive functions}
We also conduct sampling to our redundancy analysis for recursive functions.
For a recursive function, we first create an instrumented clone copy of 
the whole function body.
We then add a sampling-control code snippet at the entry point of the function,
where \texttt{CurrentID} and \texttt{NextSampleID} are maintained to decide
whether to execute the original function body or the instrumented 
value-recording clone copy.
We also create clones for all the callee functions of the recursive function
under study, so that the sampling decision can be correctly conducted
throughout the call chain.

@@

Second, we identify and avoid monitoring some memory reads whose return values 
can be statically proved to be different throughout one loop instance in 
cross-iteration redundancy analysis.
Specifically, for read on loop induction variable, such as i for loop at line 12 of Figure~\ref{fig:Apache34464}, 
%Specifically, reading of loop induction 
%variables, such as XXX, are always identified as source instructions in % variable i for loop at line 12
%cross-iteration redundancy analysis; 
we also know for sure that their return
values are different in different iterations. 
If source instructions include read on loop induction variables, we know that 
there could not be cross-iteration redundancy. 
We use scalar evolution analysis
provided by LLVM to identify induction variables and avoid tracking their
values.
%induction variables are not alwayes identified as source instructions.
%it could be possible that side-effect instructions do not depend on induction variables.
%for example, side-effect instruction may only depend on array content, and array index 
%will not be source instructions

%TODO: Linhai, I find it hard to believe that consider "there will not be
%cross-iteration redundancy simply because induction variable is in the 
%dependent set. Really? The input workload itself could be repititive, and hence
%could still deserve monitoring, right? 
%

@@

Third, sometimes we only record the memory-address range of a sequence of memory
read, instead of the value returned by every read, in cross-loop redundancy
analysis. 
The loop at line 12 in Figure~\ref{fig:Apache34464} shows an example.
The content of array \texttt{source} is never modified
throughout the outer-loop, which starts 
at line 12 in the Figure~\ref{fig:Apache34464}.
%We do not have the static analysis to prove the content of array does not change.
%for source[i] for the loop at line 12, we only need to record source, initial value of i and final value of i. 
%TODO
%Do you really do analysis to prove that the source array is not changed?
%ANSWER
%Shan, I do not have invariant analysis to prove the the source array is not changed.
%I remove that part of writing in the last version I sent to you. 
%It is very difficult to implement the invariant analysis.
%I plan to discuss this in limitation part of this section, and say that this could bring false positives.
%There are reasons why I feel it is too difficult to implement the invariant analysis:
%1. it is difficult to find the range (the outer loop) to apply the analysis.
%assume we have loopA, loopB and loopC. loopA contains loopB, and loopB contains loopC. 
%we are analyzing loopC. It could be possible that loopB only execute 1 or 2 iterations, and loopA is the real outer loop
%2. It is very difficult to prove that there is no other loop inside the outer loop which does not write to the same array.
%There could be cases like:
% for(i = 0; i < 10; i++)
%   func(&(A[i]));
% func will write to its parameter.
Therefore, to check whether different inner loop instances read similar
sequence of array data, we only need to record the starting and 
ending array index touched by each inner loop, significantly reduce the 
monitoring overhead. To accomplish this optimization, we again leverage
the scalar evolution analysis provided by LLVM. The scalar evolution analysis
tells us whether the address of a memory read instruction
is a loop induction variable. For example, the address for memory read \texttt{source[i]} is added by one in each loop iteration,
so it is a loop induction variable. 
From the scalar evolution analysis, we know that the starting address is \texttt{source} plus the initial value of \texttt{i}, and the ending address
is source plus the ending value of \texttt{i}.  
%TODO Linhai, I don't understand your original text. The address is 
%source+i; loop induction variable is i. What do you mean by "the read address
%is an induction varaible"? Please rewrite.

%ANSWER
%Shan, both source + i and i are induction variables, becasue both of them 
%will be added by 1 in each iteration. The only difference between these two 
%are their initial values.
%For cross-loop redundant bugs, we also rely on scalar evolution analysis to identify whether the read address
%is an induction variable for each monitored read instruction.

>>>>

\emph{How to judge redundancy between two iterations/loop-instances?}
Given two iterations (or loop-instances) $i_1$ and $i_2$, since they have 
the same source code, 
a naive, yet expensive, solution is to record and compare the return value of
every memory read conducted by $i_1$ and $i_2$. Two better alternative
solutions are to record and compare only the values written by the
side-effect instructions, such as 
line 9 in Figure~\ref{fig:Mozilla477564},
or read by 
the source instructions\footnote{We define source instructions in a code
region $r$ as a set of memory-read instructions that side-effect
instructions in $r$ depend on and do not depend on any other instructions
inside $r$.}, 
such as source[i] at line 12 of Figure~\ref{fig:Apache34464}.

Among the the above two potential solutions, our design chooses the second one,
because it is
more informative for performance diagnosis 
to track the cause rather than the effect.

\emph{How to handle partial redundancy?}
In practice, redundant loops may be doing largely the same, but not exactly
the same, computation across iterations or loop instances. 
%It is also possible
%TODO define loop instance.
%that only some, instead of all, iterations in a loop are doing redundant
%computation. 
We will discuss how we handle this issue in Section \ref{sec:cal}.

\emph{How to lower the overhead of record-and-compare?}
Even if we only record and compare the values returned by source instructions
the run-time overhead and the log size
could still be large. We will use static analysis and run-time sampling
to lower this time and spatial
overhead 
(Section \ref{sec:inst} and \ref{sec:perf}).
%TODO static analysis alone is not sufficient, because some redundant is
%workload dependent

\emph{How to provide the most suitable fix-strategy suggestion?}
Finally, as discussed in Section \ref{sec:study_ob} and Table \ref{tab:root},
memoization and batching are both common fix strategies for redundant loops.
To pick the right fix strategies,
extra analysis is conducted by \Tool and presented in 
Section \ref{sec:redundant_fix}.

@@

After identifying source instructions, we instrument them to record
what values they read from memory
at run time.
%Specifically, we will assign
%a unique ID for each source instruction, and a pair of $<InstID, Value>$
%will be recorded at run time with the execution of a source instruction.
Our trace also includes some delimiters and meta information that allows
trace analysis to differentiate values recorded from different instructions, 
loop
iterations, loop instances, and so on.
%TODO
%All values defined outside the loop is recorded in block O. 
%We record a delimiter, loop instance number and values defined in previous iterations in block H1'.
%Since we only consider redundant iterations from the same loop instance,  
%we do not record values defined outside the loop for cross-iteration redundancy.

@@

\paragraph{High-level algorithms}
For cross-iteration redundancy, we need to answer two questions. 
First, how to judge whether
two iterations are doing redundant work?
Second, is a (dynamic) loop problematic when it contains only few 
iterations that are
redundant with each other?

Our answer to these two questions stick to one principle: there should be
sufficient amount of redundant computation to make a loop likely root-cause
for a user-perceived performance problem and to make itself worthwhile to
get optimized by the developers. Consequently,
for the first question, \Tool takes a strict 
definition --- only iterations that are doing exactly the same computation are
considered redundant. Since one iteration may not contain too much computation,
a weaker definition here may lead to many false positives. For the 
second question, we believe there should be a threshold. In our current 
prototype,
when the number of distinct iterations is less than half of the total iterations, 
we consider the loop to be cross-iteration redundant. 
%when the number of distinct iterations is less than half of the total iterations 
%iterations/(distinct iterations) = 2

@@

For example, Figure~\ref{fig:Apache37184} shows a loop from Apache-Ant that
contains cross-iteration redundancy.
Under the problem triggering input, there are
only few distinct listeners, and most of the
loop iterations in \texttt{fireMessageLoggedEvent}
are doing redundant work. 
%The problem for this bug is that developers say that the performance 
%loss happens in fireMessageLoggedEvent, but in the code I found, function
%messageLogged does not contain anything, and it is an empty function.
%I guess either developers do not have correct understanding of this bug,
%or I did not find the correct codes.

@@

The implementation of checking cross-loop redundancy goes through several
steps. First, for $k$ dynamic instances of a static loop $L$ that appear
at run time, denoted as $l_1$, $l_2$,
..., $l_k$, we check whether redundancy exists between $l_1$ and $l_2$, 
$l_2$ and $l_3$, and so on. Second, we compute a 
\textit{cross-loop redundancy rate} for $L$
--- dividing the number of redundant pairs by $k-1$.
The smaller the rate is, with 0 being the minimum possible value, the
less cross-loop redundancy $L$ contains.
Here we only check redundancy between consecutive loop instances, because  
checking the redundancy between every pairs of loop
instances is time consuming.

@@

\paragraph{Cross-loop redundancy analysis} 
At high level, we randomly decide at the beginning
of every loop instance whether to track values for this instance. 
Since we will need to compare two consecutive loop
instances for redundancy, once we decide to sample one loop instance, we will
make sure to sample the immediately next loop instance too.
The implementation is straightforward by cloning the whole loop and making
sampling decisions in the loop pre-headers.
%; (2)
%sampling is conducted when \texttt{CurrentID} equals either
%\texttt{NextSampleID} or \texttt{NextSampleID}$+1$, with \texttt{NextSampleID}
%increased by a random value in the latter case.

@@

%\paragraph{Handling recursive functions}
%We also conduct sampling to our redundancy analysis for recursive functions.
%For a recursive function, we first create an instrumented clone copy of 
%the whole function body.
%We then add a sampling-control code snippet at the entry point of the function,
%where \texttt{CurrentID} and \texttt{NextSampleID} are maintained to decide
%whether to execute the original function body or the instrumented 
%value-recording clone copy.
%We also create clones for all the callee functions of the recursive function
%under study, so that the sampling decision can be correctly conducted
%throughout the call chain.

@@

Second, we identify and avoid monitoring some memory reads whose return values 
can be statically proved to be different throughout one loop instance in 
cross-iteration redundancy analysis.
Specifically, for read on loop induction variable, such as i for loop at line 12 of Figure~\ref{fig:Apache34464}, 
%Specifically, reading of loop induction 
%variables, such as XXX, are always identified as source instructions in % variable i for loop at line 12
%cross-iteration redundancy analysis; 
we also know for sure that their return
values are different in different iterations. 
If source instructions include read on loop induction variables, we know that 
there could not be cross-iteration redundancy. 
We use scalar evolution analysis
provided by LLVM to identify induction variables and avoid tracking their
values.
%induction variables are not always identified as source instructions.
%it could be possible that side-effect instructions do not depend on induction variables.
%for example, side-effect instruction may only depend on array content, and array index 
%will not be source instructions

%TODO: Linhai, I find it hard to believe that consider "there will not be
%cross-iteration redundancy simply because induction variable is in the 
%dependent set. Really? The input workload itself could be repetitive, and hence
%could still deserve monitoring, right? 
%

@@

Third, sometimes we only record the memory-address range of a sequence of memory
read, instead of the value returned by every read, in cross-loop redundancy
analysis. 
The loop at line 12 in Figure~\ref{fig:Apache34464} shows an example.
The content of array \texttt{source} is never modified
throughout the outer-loop, which starts 
at line 12 in the Figure~\ref{fig:Apache34464}.
%We do not have the static analysis to prove the content of array does not change.
%for source[i] for the loop at line 12, we only need to record source, initial value of i and final value of i. 
%TODO
%Do you really do analysis to prove that the source array is not changed?
%ANSWER
%Shan, I do not have invariant analysis to prove the the source array is not changed.
%I remove that part of writing in the last version I sent to you. 
%It is very difficult to implement the invariant analysis.
%I plan to discuss this in limitation part of this section, and say that this could bring false positives.
%There are reasons why I feel it is too difficult to implement the invariant analysis:
%1. it is difficult to find the range (the outer loop) to apply the analysis.
%assume we have loopA, loopB and loopC. loopA contains loopB, and loopB contains loopC. 
%we are analyzing loopC. It could be possible that loopB only execute 1 or 2 iterations, and loopA is the real outer loop
%2. It is very difficult to prove that there is no other loop inside the outer loop which does not write to the same array.
%There could be cases like:
% for(i = 0; i < 10; i++)
%   func(&(A[i]));
% func will write to its parameter.
Therefore, to check whether different inner loop instances read similar
sequence of array data, we only need to record the starting and 
ending array index touched by each inner loop, significantly reduce the 
monitoring overhead. To accomplish this optimization, we again leverage
the scalar evolution analysis provided by LLVM. The scalar evolution analysis
tells us whether the address of a memory read instruction
is a loop induction variable. For example, the address for memory read \texttt{source[i]} is added by one in each loop iteration,
so it is a loop induction variable. 
From the scalar evolution analysis, we know that the starting address is \texttt{source} plus the initial value of \texttt{i}, and the ending address
is source plus the ending value of \texttt{i}.  
%TODO Linhai, I don't understand your original text. The address is 
%source+i; loop induction variable is i. What do you mean by "the read address
%is an induction variable"? Please rewrite.

%ANSWER
%Shan, both source + i and i are induction variables, because both of them 
%will be added by 1 in each iteration. The only difference between these two 
%are their initial values.
%For cross-loop redundant bugs, we also rely on scalar evolution analysis to identify whether the read address
%is an induction variable for each monitored read instruction.
